\section{Project: The Chermak--Delgado subgroup}

\begin{definition}
\index{Chermak--Delgado!measure}
Let $G$ be a finite group and $H$ a subgroup of $G$. 
The \emph{Chermak--Delgado measure} of $H$ 
is the number 
$m_G(H)=|H||C_G(H)|$.
\end{definition}

\begin{example}
If $G$ is abelian and $H$ is a subgroup of $G$, then 
$m_G(H)=|H||G|$.
\end{example}

\begin{example}
Let $G=\Sym_3$. The subgroups of $G$ are 
	\[
		H_0=1,\quad
		H_1=\langle (23)\rangle,\quad
		H_2=\langle (12)\rangle,\quad
		H_3=\langle (13)\rangle,\quad
		H_4=\langle (123)\rangle,\quad
		H_5=\Sym_3.
	\]
	A direct calculation shows that 
	\[
		m_G(H_j)=\begin{cases}
			6 & \text{if $j\in\{0,5\}$},\\
			4 & \text{if $j\in\{1,2,3\}$},\\
			9 & \text{if $j=4$}.
		\end{cases}
	\]
\end{example}

\begin{lemma}
\label{lem:CD1}
Let $G$ be a finite group and $H$ be a subgroup of $G$. Then 
\[
m_G(H)\leq m_G(C_G(H)).
\]
If the equality holds, then $H=C_G(C_G(H))$.
\end{lemma}

\begin{proof}
Let $C=C_G(H)$. 
Since $H\subseteq C_G(C)$, 
\[
m_G(C)=|C||C_G(C)|\geq |C||H|=m_G(H). 
\]
If $m_G(H)=m_G(C_G(H))$, then $|H|=|C_G(C_G(H))|$ and 
hence $H=C_G(C_G(H))$, as $H\subseteq C_G(C_G(H))$. 
\end{proof}

\begin{lemma}
	Let $G$ be a finite group and 
	$H$ and $,K$ be subgroups of $G$. Let $D=H\cap K$ and
    $J=\langle H,K\rangle$. Then 
	\[
		m_G(H)m_G(K)\leq m_G(D)m_G(J).
	\]
	If the equality holds, then $J=HK$ and $C_G(D)=C_G(H)C_G(K)$.
	\label{lem:CD2}
\end{lemma}

\begin{proof}
	Let $C_H=C_G(H)$, $C_K=C_G(K)$, $C_D=C_G(D)$, and $C_J=C_G(J)$. Then
	$C_J=C_H\cap C_K$ and $C_H\cup C_K\subseteq C_D$. Since 
	\[
		|J|\geq |HK|=\frac{|H||K|}{|D|},
		\quad
		|C_D|\geq |C_HC_K|=\frac{|C_H||C_K|}{|C_J|},
	\]
	we obtain that 
	\[
		m_G(D)
		=|D||C_D|\geq \frac{|H||K|}{|J|}\frac{|C_H||C_K|}{|C_J|}
		=\frac{m_G(H)m_G(K)}{m_G(J)}.
	\]
	The second claim is clear. 
\end{proof}

\begin{definition}
\index{Lattice of subgroups}
Let $G$ be a finite group and $\mathcal{L}$ be a collection of subgroups of $G$. We say that $\mathcal{L}$ is a \emph{lattice} if for every $H,K\in\mathcal{L}$ one has that
$H\cap K\in\mathcal{L}$ and $\langle H,K\rangle\in\mathcal{L}$. 
\end{definition}

Since $G$ is finite, it makes sense to consider the set $\mathcal{L}(G)$ of 
subgroups of $G$ $G$ where the Chermak--Delgado gets its largest value,
say $M_G$. 

\begin{exercise}
	\label{xca:M_S}
	Let $G$ be a finite group and $H$ be a subgroup of $G$. Prove that 
	$M_H\leq M_G$.
\end{exercise}

% \begin{svgraybox}
% 	Sabemos que existe algún subgrupo $K$ de $H$ tal que $M_H=m_H(K)$. Como
% 	$C_H(K)\subseteq C_G(K)$, 
% 	\[
% 		M_H=m_H(K)=|H||C_H(K)|\leq |H||C_G(K)|\leq m_G(H)\leq M_G.
% 	\]
% \end{svgraybox}

\begin{example}
	\label{exa:D8_CD}
    Let $G=\D_8=\langle r,s:r^4=s^2=1,srs=r^{-1}\rangle$ be the dihedral group
    of eight elements. In the subgroups 
    \[
		G,
		\quad
		Z(G)=\{1,r^2\},\quad
		A=\{1,r,r^2,r^3\},\quad
		B=\{1, s,sr^2,r^2\},\quad
		C=\{1,sr,sr^3,r^2\},
	\]
	the Chermak--Delgado measure is $16$ and this is the largest possible value. Thus and $M_G=16$ and $\mathcal{L}(G)=\{G,Z(G),A,B,C\}$. 
	\begin{lstlisting}
gap> ChermakDelgado := function(group, subgroup)
> return Size(subgroup)\
> *Size(Centralizer(group, subgroup));
> end;
function( group, subgroup ) ... end
gap> gr := DihedralGroup(IsPermGroup, 8);;
gap> r := gr.1;;
gap> s := gr.2;;
gap> ChermakDelgado(gr, Subgroup(gr, [r]));
16
gap> ChermakDelgado(gr, Subgroup(gr, [s*r,s*r^3]));
16
gap> ChermakDelgado(gr, Subgroup(gr, [s,s*r^2]));
16
gap> ChermakDelgado(gr, Subgroup(gr, [r^2]));
16
gap> List(AllSubgroups(gr), x->ChermakDelgado(gr, x));
[ 8, 16, 8, 8, 8, 8, 16, 16, 16, 16 ]
	\end{lstlisting}
\end{example}

\begin{theorem}
	Let $G$ be a finite group. The following statements hold: 
	\begin{enumerate}
		\item $\mathcal{L}(G)$ is a lattice. 
		\item If $H,K\in\mathcal{L}(G)$, then $\langle H,K\rangle=HK$.
		\item If $H\in\mathcal{L}(G)$, then $C_G(H)\in\mathcal{L}(G)$ and $C_G(C_G(H))=H$.
	\end{enumerate}
	\label{thm:lattice}
\end{theorem}

\begin{proof}
	If $H,K\in\mathcal{L}(G)$, then $m_G(H)=m_G(K)=M_G$. Let $D=H\cap K$ and $J=\langle
	H,K\rangle$. By Lemma~\ref{lem:CD2}, 
	\[
		M_G^2=m_G(H)m_G(K)\leq m_G(D)m_G(J).
	\]
	Since $m_G(D)\leq M_G$ and $m_G(J)\leq M_G$ (because $M_G$ is the largest possible value), we conclude that $m_G(D)=m_G(J)=M_G$. Hence $\mathcal{L}(G)$ is a lattice. 

	Since $m_G(H)m_G(K)=m_G(D)m_G(J)=M_G^2$, Lemma~\ref{lem:CD2} implies that 
	$J=HK$. 

	By Lemma~\ref{lem:CD1}, 
	\[
	M_G=m_G(H)\leq m_G(C_G(H)).
	\]
	Since $M_G$ is the largest possible value, $m_G(C_G(H))=M_G$. Thus 
    $C_G(H)\in\mathcal{L}(G)$.  By Lemma~\ref{lem:CD1}, $C_G(C_G(H))=H$.
\end{proof}

\index{Chermak--Delgado!subgroup}
Theorem~\ref{thm:lattice} implies the existence 
of the \emph{Chermak--Delgado subgroup}.

\begin{corollary}
	\label{cor:ChermakDelgado}
	Let $G$ be a finite group. There exists a unique subgroup $M$ minimal 
    suc that $m_G(M)$ is the largest possible value among all the subgroups 
    of $G$. Moreover, $M$ is characteristic, abelian and $Z(G)\subseteq M$. 
\end{corollary}

% f(C_G(H))=C_G(f(H))$ para todo $H$ y todo $f\in\Aut(G)$.

\begin{proof}
	By Theorem~\ref{thm:lattice}, $\mathcal{L}(G)$ is a lattice. Let 
	\[
		M=\bigcap_{H\in\mathcal{L}(G)}H\in\mathcal{L}(G).
	\]
	By Theorem~\ref{thm:lattice},  
	\[
    C_G(M)\in\mathcal{L}(G)
    \text{ and }M=C_G(C_G(M))\supseteq Z(G).
    \]Since $C_G(M)\in\mathcal{L}(G)$, $M\subseteq C_G(M)$. Hence $M$ is abelian. Moreover, $M$ is characteristic in $G$ because $f(M)\in\mathcal{L}(G)$
	for all $f\in\Aut(G)$.
\end{proof}

\begin{example}
	Let $G=\D_8$ be the dihedral group of eight elements. The Chermak--Delgado subgroup of $G$ is $Z(G)\simeq C_2$. See Example~\ref{exa:D8_CD}.
\end{example}

\begin{theorem}[Chermak--Delgado]
	\index{Chermak--Delgado!theorem}
 	\label{thm:ChermakDelgado}
	Let $G$ be a finite group. Then $G$ has an abelian characteristic subgroup $M$ such that $(G:M)\leq (G:A)^2$ for every abelian subgroup 
	$A$ of $G$. 
\end{theorem}

\begin{proof}
	Let $M$ be the Chermak--Delgado subgroup of Corollary~\ref{cor:ChermakDelgado} 
    and $A$ be an abelian subgroup of 
	$G$. Then $A\subseteq C_G(A)$. Hence 
	\[
		m_G(M)\geq m_G(A)=|A||C_G(A)|\geq|A|^2
	\]
	and 
	\[
	(G:A)^2
	=\frac{|G|^2}{|A|^2}\geq\frac{|G|^2}{m_G(M)}
	=\frac{|G|}{|M|}\frac{|G|}{|C_G(M)|}
	=\frac{|G|}{|M|}
	=(G:M).\qedhere 
	\]
\end{proof}

\begin{corollary}
	Let $G$ be a non-abelian finite group and $H$ be a subgroup of $G$ such that 
	\[
	|H||C_G(H)|>|G|.
	\]
	Then $G$ is not simple. 
\end{corollary}

\begin{proof}
	Let $M$ be the Chermak--Delgado subgroup of $G$. 
	Then 
	\begin{equation}
		\label{equation:mG}
	m_G(M)\geq m_G(H)>|G|.
	\end{equation}
	This implies that $M\ne\{1\}$, since $m_G(M)=m_G(1)=|G|$. If $G$ is simple, then $G=M$ is abelian. 
\end{proof}

\begin{corollary}
	Let $G$ be a non-abelian finite group and $P\in\Syl_p(G)$. If $P$ is abelian and $|P|^2>|G|$, then $G$ is not simple. 
\end{corollary}

\begin{proof}
	Let $M$ be the Chermak--Delgado subgroup of $G$. Since $P$ is abelian, 
    \[
    (G:M)\leq (G:P)^2<|G|
    \]
    by Theorem~\ref{thm:ChermakDelgado}. Hence 
    $M\ne\{1\}$. If $G$ is simple, then $G=M$ is abelian. 
\end{proof}

We now discuss an application of the Wielandt zipper theorem 
to the Chermak--Delgado lattice. 

\begin{lemma}
	\label{lem:L(G)L(S)}
	Let $G$ be a finite group, $H\in\mathcal{L}(G)$ and  $S$ be a subgroup of $G$ such that 
	$HC_G(H)\subseteq S$. Then $H\in\mathcal{L}(S)$.
\end{lemma}

\begin{proof}
	Since $C_G(H)\subseteq S$, $C_G(H)=C_S(H)$. By Exercise~\ref{xca:M_S},
    $M_S\leq M_G$. Thus $M_G=M_S$, since 
	\[
		M_G=m_G(H)=|H||C_G(H)|=|H||C_S(H)|=m_S(H)\leq M_S.\qedhere 
	\]
\end{proof}

\begin{theorem}
	\label{thm:L(G)subnormal}
	Let $G$ be a finite group. Every $H\in\mathcal{L}(G)$ is subnormal in $G$.
\end{theorem}

\begin{proof}
	We proceed by induction on $|G|$. If $|G|=1$, the result is trivial. So assume the group $G$ is non-trivial. Let $H\in\mathcal{L}(G)$ and $K=HC_G(H)$. Since $H$ is normal in $K$, by the inductive hypothesis, 
    it is enough to show that 
	$K$ is subnormal in $G$. If $K=G$, the claim holds. So assume that 
	$K\ne G$. 

	Assume that $K$ is not subnormal in $G$. By the inductive hypothesis and 
    Wielandt's zipper theorem (Theorem~\ref{thm:zipper}), there exists a unique 
    maximal subgroup $M$ containing $K$. By Theorem~\ref{thm:lattice},
	$C_G(H)\in\mathcal{L}(G)$ and $K=HC_G(H)\in\mathcal{L}(G)$. By Lemma~\ref{lem:L(G)L(S)},
	$H\in\mathcal{L}(M)$. Hence $K\in\mathcal{L}(M)$. By the inductive hypothesis, $K$ is subnormal in $M$. We claim that $M$ is normal in $G$. Let $x\in G$. Since 
	$m_G(xKx^{-1})=m_G(K)$, the subgroup $xKx^{-1}\in\mathcal{L}(G)$. Hence 
	$K(xKx^{-1})\in\mathcal{L}(G)$. 
	
	If $K(xKx^{-1})=G$, then, since there exist $k_1,k_2\in K$ such that 
	$k_1(xk_2x^{-1})=x^{-1}$, we obtain that $x\in K$, since $x^{-1}=k_2k_1\in K$. This implies that $xKx^{-1}\subseteq K$. Therefore $K=G$, a contradiction.

	Since $K(xKx^{-1})\ne G$, there exists a maximal subgroup $N$ such that 
	$K(xKx^{-1})\subseteq N$. Since $K\subseteq N$, $N=M$ because $M$ is the unique
	maximal subgroup containing $K$. Since $xKx^{-1}\subseteq M$, $K\subseteq
	x^{-1}Mx$. Hence $x^{-1}Mx=M$, because $x^{-1}Mx$ is a maximal subgroup containing $K$ and $M$ is the only maximal subgroup containing $K$. 
\end{proof}

\begin{corollary}
	Let$G$ be a non-abelian finite Then $\mathcal{L}(G)=\{1,G\}$. 
\end{corollary}

\begin{proof}
	Let $K\in\mathcal{L}(G)$. Then $K$ is subnormal in $G$ by Theorem~\ref{thm:L(G)subnormal}. Hence $K\in\{1,G\}$. Now the claim follows from $m_G(1)=m_G(G)$. 
\end{proof}

\begin{exercise}
	Let $n\geq5$. Prove that $\mathcal{L}(\Sym_n)=\{1,\Sym_n\}$. 
\end{exercise}

% \begin{proof}
% 	Let $G=\Sym_n$ y sea $K\in\mathcal{L}(G)$. Por el
% 	teorema~\ref{thm:L(G)subnormal}, $K$ es subnormal en $G$. Si $K\ne G$
% 	entonces se tiene una sucesión estrictamente creciente de subgrupos 
% 	\[
% 	K=K_1\triangleleft
% 	K_2\triangleleft\cdots\triangleleft K_{n-1}\triangleleft K_n=G.
% 	\]
% 	Como $K_{n-1}$ es normal en $G$, $K_{n-1}\in\{1,\Alt_n\}$ y luego $K=1$. 
% 	El corolario queda demostrado al observar que $m_G(1)=m_G(G)$. 
% \end{proof}

