\section{Project: It\^o's factorization theorem}

\begin{definition}
\index{Group!metabelian}
A group $G$ is said to be \emph{metabelian} if $[G,G]$ is abelian. 
\end{definition}

\begin{exercise}
\label{xca:metabelian1}
Prove that a group $G$ is metabelian if and only if there exists a normal 
subgroup $K$ of $G$ such that $K$ and $G/K$ are abelian.
\end{exercise}

% \begin{remark}
% 	Los grupos metabelians son solvables pues 
% 	si $G$ is metabelian entonces 
% 	$G\supseteq [G,G]\supseteq 1$ is una serie solvable para $G$.
% \end{remark}

\begin{exercise}
\label{xca:metabelian2}
Let $G$ be a metabelian group. Prove the following statements: 
\begin{enumerate}
\item If $H$ is a subgroup of $G$, then $H$ is metabelian.
\item If $f\colon G\to H$ is a group homomorphism, then $f(G)$ is metabelian. 
\end{enumerate}
\end{exercise}

\begin{lemma}
In a group, the following formulas hold:
\begin{enumerate}
	\item $[a,bc]=[a,b]b[a,c]b^{-1}$. 
	\item $[ab,c]=a[b,c]a^{-1}[a,c]$.
\end{enumerate}
\end{lemma}

\begin{proof}
This is a straightforward calculation:
\begin{align*}
&[a,b]b[a,c]b^{-1}=aba^{-1}b^{-1}baca^{-1}c^{-1}b^{-1}=abca^{-1}c^{-1}b^{-1}=[a,bc],\\
&a[b,c]a^{-1}[a,c]=abcb^{-1}c^{-1}a^{-1}aca^{-1}c^{-1}=abcb^{-1}a^{-1}c^{-1}=[ab,c].\qedhere
\end{align*}
\end{proof}

\begin{example}
The group $\Sym_3$ is metabelian, as $\Alt_3\simeq C_3$ is a normal subgroup 
and the quotient $\Sym_3/\Alt_3\simeq C_2$ an abelian group. 
\end{example}

\begin{example}
The group $\Alt_4$ is metabelian, as the normal subgroup
\[
K=\{\id,(12)(34),(13)(24),(14)(23)\}
\]
is abelian and the quotient 
$\Alt_4/K\simeq C_3$ is abelian.
\end{example}

\begin{example}
The group $\SL_2(3)$ is not metabelian, as $[\SL_2(3),\SL_2(3)]\simeq Q_8$ 
is not abelian: 
\begin{lstlisting}
gap> IsAbelian(DerivedSubgroup(SL(2,3)));
false
gap> StructureDescription(DerivedSubgroup(SL(2,3)));
"Q8"
\end{lstlisting}
\end{example}

\begin{theorem}[It\^o]
\label{thm:Ito}
\index{It\^o's factorization theorem}
Let $G=AB$ be a factorization of $G$ with $A$ and $B$ abelian 
subgroups of $G$. Then $G$ is metabelian.
\end{theorem}

\begin{proof}
Since $G=AB$ is a group, $AB=BA$. We claim that $[A,B]$ is a normal subgroup 
of $G$. Let $a,\alpha\in A$ and $b,\beta\in B$. Let  $a_1,a_2\in A$ and 
	$b_1,b_2\in B$ be such that $\alpha b\alpha^{-1}=b_1a_1$, $\beta
	a\beta^{-1}=a_2b_2$. Since 
	\begin{align*}
		&\alpha[a,b]\alpha^{-1}=a(\alpha b\alpha^{-1})a^{-1}(\alpha b^{-1}\alpha^{-1})=ab_1a_1a^{-1}a_1^{-1}b_1^{-1}=[a,b_1]\in [A,B]\\
		&\beta[a,b]\beta^{-1}=(\beta a\beta^{-1})\beta b\beta^{-1}(\beta a^{-1}\beta^{-1})b^{-1}=a_2b_2bb_2^{-1}a_2^{-1}b^{-1}=[a_2,b]\in [A,B],
	\end{align*}
	it follows that $[A,B]$ is normal in $G$. 

	We now claim that $[A,B]$ is abelian. Since 
	\begin{align*}
		&\beta\alpha[a,b]\alpha^{-1}\beta^{-1} = \beta[a,b_1]\beta^{-1}=(\beta a\beta^{-1})b_1(\beta a^{-1}\beta^{-1})b_1^{-1}=[a_2,b_1],\\
		&\alpha\beta[a,b]\beta^{-1}\alpha^{-1} = \alpha[a_2,b]\alpha^{-1}=a_2(\alpha b\alpha^{-1})a_2^{-1}(\alpha b\alpha^{-1})=[a_2,b_1],
	\end{align*}
	a direct calculation shows that 
	\[
		[\alpha^{-1},\beta^{-1}][a,b][\alpha^{-1},\beta^{-1}]^{-1}=[a,b].
	\]
	Two arbitrary generators of $[A,B]$ commute, so the group $[A,B]$ is abelian. 
	
	To finish the proof, note that $[G,G]=[A,B]$. In fact, 
	\[
	[a_1b_1,a_2b_2]=a_1[a_2,b_1]^{-1}a_1^{-1}a_2[a_1,b_2]a_2^{-1}\subseteq [A,B],
	\]
	as $[A,B]$ is normal in $G$. 
\end{proof}

In 1988 Sysak proved the following generalization 
of It\^o's theorem.  

\begin{theorem}[Sysak]
\label{thm:Sysak}
\index{Sysak's theorem}
    Let $A$ and $B$ be abelian subgroups of $G$. If $H$ is a subgroup of 
    $G$ contained in 
    $AB$, then $H$ is metabelian. 
\end{theorem}

For the proof, see \cite{MR988177}.
